Attractive people, Attractive jobs 

### 2024-04-22 paper/Attractive_people,_Attractive_jobs.qmd
Update Attractive_people,_Attractive_jobs.qmd

---
title: "Attractive people, Attractive jobs "
subtitle: "The influence of attractiveness on Employment in the United States (2023)"
author: Sky Suh
thanks: "Code and data are available at: https://github.com/sjp2023/beauty-standard.git"
date: today
date-format: long
abstract: "This paper delves into the relationship between attractiveness and employment, exploring how various factors such as individual characteristics, skills, and demographics intersect with physical appearance, educational background and gender to influence the hiring process and subsequent career success. Our study makes use of data sourced from the University of Toronto dataverse, and reveals interesting insights into the role of attractiveness in shaping employment outcomes and the status of jobs. Our findings suggest that most socio-demographic attractiveness including appearance, education and sex can have a significant impact on both the hiring process and long-term career, highlighting its relevance in employment and hiring sessions. Additionally, this paper emphasizes the importance of considering a broader range of factors beyond attractiveness alone when predicting employment outcomes as physical, educational background and gender with the correlation fo those variables."
format: pdf
toc: TRUE
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Attractive people, Attractive jobs "
subtitle: "The influence of attractiveness on Employment in the United States (2023)"
author: Sky Suh
thanks: "Code and data are available at: https://github.com/sjp2023/beauty-standard.git"
date: today
date-format: long
abstract: "This paper delves into the relationship between attractiveness and employment, exploring how various factors such as individual characteristics, skills, and demographics intersect with physical appearance, educational background and gender to influence the hiring process and subsequent career success. Our study makes use of data sourced from the University of Toronto dataverse, and reveals interesting insights into the role of attractiveness in shaping employment outcomes and the status of jobs. Our findings suggest that most socio-demographic attractiveness including appearance, education and sex can have a significant impact on both the hiring process and long-term career, highlighting its relevance in employment and hiring sessions. Additionally, this paper emphasizes the importance of considering a broader range of factors beyond attractiveness alone when predicting employment outcomes as physical, educational background and gender with the correlation of those variables."
format: pdf
toc: TRUE
number-sections: true
bibliography: references.bib
---
